A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-28 main.Rmd
Section 6

```{r carrier-mosaic, fig.cap = "(ref:carrier-mosaic-cap)", fig.pos="b"}
```

@@

```{r flight-pipeline1, fig.cap = "(ref:flight-pipeline1-cap)", fig.pos="t"}
include_graphics("img/flight-pipeline1")
```

@@

```{r sel-monthly-plot, fig.cap = "(ref:sel-monthly-plot-cap)", fig.height = 7, fig.pos="t"}
```

@@

```{r flight-pipeline3, fig.cap = "(ref:flight-pipeline3-cap)", fig.pos="!htb"}
include_graphics("img/flight-pipeline3")
```

>>>>

```{r carrier-mosaic, fig.cap = "(ref:carrier-mosaic-cap)"}
```

@@

```{r flight-pipeline1, fig.cap = "(ref:flight-pipeline1-cap)"}
include_graphics("img/flight-pipeline1")
```

@@

```{r sel-monthly-plot, fig.cap = "(ref:sel-monthly-plot-cap)", fig.height = 7}
```

@@

```{r flight-pipeline3, fig.cap = "(ref:flight-pipeline3-cap)"}
include_graphics("img/flight-pipeline3")
```
